TIMES Ireland Model: Residential Sector

### 2021-03-23 manuscript.tex
Done for the day, in progress

\usepackage{lineno}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{float}
\usepackage{longtable}
\usepackage{threeparttable}
\usepackage{biblatex}
\addbibresource{references.bib} %Imports bibliography file

\usepackage[subpreambles=true]{standalone}
\usepackage{import}

\usepackage[utf8]{inputenc}
\usepackage[hyphens]{url}

@@

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

@@

\affiliation[inst1]{organization={Energy Policy and Modelling Group, MaREI Centre,},%Department and Organization
            addressline={Environmental Research Institute}, 
            city={Cork},
            country={Ireland}}

\affiliation[inst2]{organization={School of Engineering,},%Department and Organization
            addressline={University College Cork}, 
            city={Cork},
            country={Ireland}}

@@

\begin{abstract}
%% Text of abstract
Under the climate action bill, the Irish government have set legally binding targets to reduce greenhouse gas (GHG) emissions by 51\% in 2030, compared to 2018 and to achieve “net-zero” GHG emissions by 2050. These legally binding targets are set, so Ireland must comply with the objective of the Paris Agreement. 
Ireland and impartiular Ireland's residential sector is preforming poorly when compared to other EU countries. Ireland has the lowest renewable heat of 6.3\% \cite{2021EurostatExplorer}
% In 2018 only 7.8% of the population of Ireland lived in flats, this is the lowest percentage in the EU-27, the second lowest was the Netherlands at 20.2% (Eurostat, 2018). The average EU-27 was 46% and the closest in comparison was the UK at 14.8% (Eurostat, 2018). Ireland has a low urbanisation percentage of 63.2%, where the European average is 74.5% and the UK is 83.4% (United Nations, Department of Economic and Social Affairs, Population Division . World Urbanization Prospects, 2018). Ireland has the 3rd largest residential living space per capita in Europe at 41.75 m2/capita, behind Denmark and Cyprus. The European average is 33.8 m2/capita (Average Floor Area per Capita, 2008). Ireland’s low urbanisation percentage has contributed to a low number of flats, and therefore a high percentage of detached, semi-detached and terrace dwellings. Ireland’s dwellings are heated primarily by individual systems sourced from fossil fuels and the large size of Ireland’s dwellings has compounded the challenge of Ireland’s settlement patterns on climate change obligations.
The Energy system optimization models (ESOMs) have been used extensively in providing insights to decision makers on issues related to climate and energy policy.

@@

%% For citations use: 
%%       \citet{<label>} ==> Jones et al. (2015)
%%       \citep{<label>} ==> (Jones et al., 2015)

>>>>

\usepackage{lineno}
\usepackage{xcolor}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{float}
\usepackage{longtable}
\usepackage{threeparttable}
\usepackage{biblatex}
\bibliography{references.bib} %Imports bibliography file

@@

@@

\affiliation[inst1]{organization={Energy Policy and Modelling Group, MaREI Centre},%Department and Organization
            addressline={Environmental Research Institute}, 
            city={Cork},
            country={Ireland}}

\affiliation[inst2]{organization={School of Engineering},%Department and Organization
            addressline={University College Cork}, 
            city={Cork},
            country={Ireland}}

@@

\begin{abstract}
%% Text of abstract
Under the climate action bill, the Irish government have set legally binding targets to reduce greenhouse gas (GHG) emissions by 51\% in 2030, compared to 2018 and to achieve “net-zero” GHG emissions by 2050 \cite{2021Climate2021}. These legally binding targets are set to ensure Ireland complies the Paris Agreement. 
Ireland and particularly Ireland's residential sector is preforming poorly. Ireland has the lowest renewable heat of 6.3\% \cite{2021EurostatExplorer}, large and poor fabric houses is hindering progress
Heat Pumps are offering a chance to change that Heat Pump renewable energy and decarbonising electricity secotr and high COPs with large rural detached settle patterns. 
% In 2018 only 7.8% of the population of Ireland lived in flats, this is the lowest percentage in the EU-27, the second lowest was the Netherlands at 20.2% (Eurostat, 2018). The average EU-27 was 46% and the closest in comparison was the UK at 14.8% (Eurostat, 2018). Ireland has a low urbanisation percentage of 63.2%, where the European average is 74.5% and the UK is 83.4% (United Nations, Department of Economic and Social Affairs, Population Division . World Urbanization Prospects, 2018). Ireland has the 3rd largest residential living space per capita in Europe at 41.75 m2/capita, behind Denmark and Cyprus. The European average is 33.8 m2/capita (Average Floor Area per Capita, 2008). Ireland’s low urbanisation percentage has contributed to a low number of flats, and therefore a high percentage of detached, semi-detached and terrace dwellings. Ireland’s dwellings are heated primarily by individual systems sourced from fossil fuels and the large size of Ireland’s dwellings has compounded the challenge of Ireland’s settlement patterns on climate change obligations.
The Energy system optimization models (ESOMs) have been used extensively in providing insights to decision makers on issues related to climate and energy policy.

@@
